---
title: "Wave 1 Statistical Analyses"
output: pdf_document
author: Marta Topor & Bertil Wegmann
date: June 2024
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rstan)
library(ggplot2)
```

# Hierarchical Bayesian Models Wave 1

This document runs the models used to analyse the main outcomes for Wave 1.   
The structure of the document follows the Analysis Plans.txt file.   
The variables and outcome variables are outlined in Meta-Data.txt.  
<!-- ADD DETAILS The STAN files with the model formulas are...--> 
  

## Data Set 1 - Binary Categorical Outcomes
  
### Crisis aware 

Bayesian Logistic regression for whether participants were aware of the reproducibility crisis or not (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN  
  -  whether the participant was in their first, second, placement or third year  
  -  interaction between the two variables above  
  
  
    
```{r Set_1 Crisis Aware}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/Set1_AllData.csv", sep = "")) 

# Prepare all objects for the model

Index <- !is.na(data$crisis_aware)
y <- data$crisis_aware[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```
The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `    
  

So the interpretation is that students who attend a UKRN affiliated university are more likely to be aware of the reproducibility crisis in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  
  
  
To see the magnitude of this difference. 
```{r Crisis Aware effect}
#could make plots for university which is in the UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 
# use the picture to calculate the numbers that will be used in the plot

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp( mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

#this should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRn status, x = current year

#!!!--------This currently does not work----------------
#Multiplication errors for the matrices and the dimensions don't match


#Next - add the matrix for mu with 20 000 rows and 1 column 

#p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]

matrix1 <- all_beta * c(X)
matrix1 <- c(all_beta) * X 



#!--------All below is old code

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_UKRN_Y1 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_UKRN_Y1 <- val_upp/(1+val_upp)


#Probability for UKRN Year 2 at 2.5% and 97.5%
#prob2.5_UKRN_Y2 <- 0
#prob97.5_UKRN_Y2 <- 0
#X <- 1 * 2 * (1*2) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_UKRN_Y2 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_UKRN_Y2 <- val_upp/(1+val_upp)


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
#prob2.5_UKRN_Y2.5 <- 0
#prob97.5_UKRN_Y2.5 <- 0
#X <- 1 * 2.5 * (1*2.5) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_UKRN_Y2.5 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_UKRN_Y2.5 <- val_upp/(1+val_upp)


#Probability for UKRN Year 3 at 2.5% and 97.5%
#prob2.5_UKRN_Y3 <- 0
#prob97.5_UKRN_Y3 <- 0
#X <- 1 * 3 * (1*3) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_UKRN_Y3 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_UKRN_Y3 <- val_upp/(1+val_upp)


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
#prob2.5_N_UKRN_Y1 <- 0
#prob97.5_N_UKRN_Y1 <- 0
#X = 0 * 1 * (1*1) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_N_UKRN_Y1 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_N_UKRN_Y1 <- val_upp/(1+val_upp)


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
#prob2.5_N_UKRN_Y2 <- 0
#prob97.5_N_UKRN_Y2 <- 0
#X = 0 * 2 * (1*2) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_N_UKRN_Y2 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_N_UKRN_Y2 <- val_upp/(1+val_upp)


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
#prob2.5_N_UKRN_Y2.5 <- 0
#prob97.5_N_UKRN_Y2.5 <- 0
#X = 0 * 2.5 * (1*2.5) # [D x D*x] 

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_N_UKRN_Y2.5 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_N_UKRN_Y2.5 <- val_upp/(1+val_upp)



#prob2.5_N_UKRN_Y3 <- 0
#prob97.5_N_UKRN_Y3 <- 0
#X = 0 * 3 * (1*3) # [D x D*x]

#val_low <- exp((mu_low+B_low)*X)
#prob2.5_N_UKRN_Y3 <- val_low/(1+val_low)

#val_upp <- exp((mu_upp+B_upp)*X)
#prob97.5_N_UKRN_Y3 <- val_upp/(1+val_upp)




#Make a data frame to plot
#cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
#                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
#                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
#                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

#colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
#cred_int$Percent <- as.factor(cred_int$Percent)

#plot(cred_int$Prob, cred_int$Year)


#ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
#  geom_point(aes(size=UKRN)) +
#  geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
#  scale_size_manual(values=c(3,3)) +
#  theme_classic()
```






### Learnt Open Science at Uni 

Bayesian Logistic regression for whether participants received teaching about open science or not (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    

```{r Set_1 OS Learnt}

Index <- !is.na(data$os_learnt)
y <- data$os_learnt[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not


x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do not cross 0.  



### Can explain open science

Bayesian Logistic regression for whether participants can explain what open science is (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    
Bayesian model for UKRN/Non-UKRN:


```{r Set_1 OS Explain}

# Logistic multilevel model simulations

Index <- !is.na(data$os_explain)
y <- data$os_explain[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do cross 0.  
 


### Applicability

Bayesian Logistic regression for whether participants think that the issues discussed in the questionnaire are relevant to them. 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    

```{r Set_1 Applicability}

# Logistic multilevel model simulations

Index <- !is.na(data$applicability)
y <- data$applicability[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000 #5000
niter <- 10000 #10 000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do cross 0.  
 
So the interpretation is that students who attend a UKRN affiliated university are not more likely to correctly explain open science.  
  


## Data Set 2 - Truncated Poisson Regression

### Awarweness Score Total

Bayesian regression for how much awareness of open and reproducible research the students had - scores range from 0 to 8. 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN  
  -  whether the participant was in their first, second, placement or third year  
  -  interaction between the two variables above  
  

```{r Total Aware}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/Set2_Awareness.csv", sep = "")) 

# Logistic multilevel model simulations

y <- data$Awareness_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

#U = 8 #the upper truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```



## Data Set 2 - Linear Regression

### Conceptual Perception Score

Bayesian regression for how much positive are students perceptions of open and reproducible research. The scores are between -2 and 2 but will be changed by adding 2.001. This way the scale will be from 0 to 4.
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN  
  -  whether the participant was in their first, second, placement or third year  
  -  interaction between the two variables above  
  

```{r Concept Perception}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/Set2_ConceptualPerception.csv", sep = "")) 

#add 2.01 to all items
#don't add 2 it can be between -2 and 2
data$Perception_Replication1 <- data$Perception_Replication1 + 2.001
data$Perception_Replication2 <- data$Perception_Replication2 + 2.001
data$Perception_Materials1 <- data$Perception_Materials1 + 2.001
data$Perception_Materials2 <- data$Perception_Materials2 + 2.001
data$Perception_Education1 <- data$Perception_Education1 +2.001
data$Perception_Education2 <- data$Perception_Education2 +2.001
data$Perception_Access1 <- data$Perception_Access1 + 2.001
data$Perception_Access2 <- data$Perception_Access2 + 2.001
data$Perception_Data1 <- data$Perception_Data1 + 2.001
data$Perception_Data2 <- data$Perception_Data2 + 2.001
data$Perception_Power1 <- data$Perception_Power1 + 2.001
data$Perception_Power2 <- data$Perception_Power2 + 2.001
data$Perception_Preregistration1 <- data$Perception_Preregistration1 + 2.001
data$Perception_Preregistration2 <- data$Perception_Preregistration2 + 2.001
data$Perception_Preprint1 <- data$Perception_Preprint1 + 2.001
data$Perception_Preprint2 <- data$Perception_Preprint2 + 2.001

data$Perception_Score_Total <- data$Perception_Replication1 + data$Perception_Replication2 + data$Perception_Materials1 + data$Perception_Materials2 + data$Perception_Education1 + data$Perception_Education2 + data$Perception_Access1 + data$Perception_Access2 + data$Perception_Data1 + data$Perception_Data2 + data$Perception_Power1 + data$Perception_Power2 + data$Perception_Preregistration1 + data$Perception_Preregistration2 + data$Perception_Preprint1 + data$Perception_Preprint2

#Better to go with the mean and have limits at -2 and 2
data$Perception_Score_Mean <- data$Perception_Score_Total/18
#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Perception_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

U = 72 #the upper truncation at value U
#! L= 0.001 # the lower truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, U=U, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```


