---
title: "Wave 1 Statistical Analyses"
output: pdf_document
author: Marta Topor & Bertil Wegmann
date: June 2024
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rstan)
library(ggplot2)
```

# Hierarchical Bayesian Models Wave 1

This document runs the models used to analyse the main outcomes for Wave 1.   
The structure of the document follows the Analysis Plans.txt file.   
The variables and outcome variables are outlined in Meta-Data.txt.  
<!-- ADD DETAILS The STAN files with the model formulas are...--> 
  

## Data Set 1 - Binary Categorical Outcomes
  
### Crisis aware 

Bayesian Logistic regression for whether participants were aware of the reproducibility crisis or not (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN  
  -  whether the participant was in their first, second, placement or third year  
  -  interaction between the two variables above  
  
  
    
Bayesian model for UKRN/Non-UKRN:  


```{r Set_1 Crisis Aware}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/Set1_AllData.csv", sep = "")) 

# Logistic multilevel model simulations

Index <- !is.na(data$crisis_aware)
y <- data$crisis_aware[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```
The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `    
  

So the interpretation is that students who attend a UKRN affiliated university are more likely to be aware of the reproducibility crisis in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  
  
  
To see the magnitude of this difference. 
```{r Crisis Aware effect}
#could make plots for university which is in the UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 
# use the picture to calculate the numbers that will be used in the plot

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#probj = exp[(muj + Bj) * X] Bj = beta1j * beta2j * beta3j X = D * x * (D*x) / 1+(exp) [muj + Bj * X]

#sort the draws 
beta1 <-  sort(ParDraws[["beta1"]])
beta2 <-  sort(ParDraws[["beta2"]])
beta3 <-  sort(ParDraws[["beta3"]])
mu_all <- sort(ParDraws[["mu"]])

#Define the beta at 2.5 and 97.5 
B_low <- beta1[500] * beta2[500] * beta3[500] #20 000 draws so for 2.5 is 500th draw
mu_low <- mu_all[500]

B_upp <- beta1[19500] * beta2[19500] * beta3[19500] #20 000 draws so for 2.5 is 500th draw
mu_upp <- mu_all[19500]

#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 at 2.5% and 97.5%
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0 
X <-  1 * 1 * (1*1) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_UKRN_Y1 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_UKRN_Y1 <- val_upp/(1+val_upp)


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- 1 * 2 * (1*2) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_UKRN_Y2 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_UKRN_Y2 <- val_upp/(1+val_upp)


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- 1 * 2.5 * (1*2.5) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_UKRN_Y2.5 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_UKRN_Y2.5 <- val_upp/(1+val_upp)


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- 1 * 3 * (1*3) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_UKRN_Y3 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_UKRN_Y3 <- val_upp/(1+val_upp)


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X = 0 * 1 * (1*1) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_N_UKRN_Y1 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_N_UKRN_Y1 <- val_upp/(1+val_upp)


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X = 0 * 2 * (1*2) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_N_UKRN_Y2 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_N_UKRN_Y2 <- val_upp/(1+val_upp)


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X = 0 * 2.5 * (1*2.5) # [D x D*x] 

val_low <- exp((mu_low+B_low)*X)
prob2.5_N_UKRN_Y2.5 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_N_UKRN_Y2.5 <- val_upp/(1+val_upp)



prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X = 0 * 3 * (1*3) # [D x D*x]

val_low <- exp((mu_low+B_low)*X)
prob2.5_N_UKRN_Y3 <- val_low/(1+val_low)

val_upp <- exp((mu_upp+B_upp)*X)
prob97.5_N_UKRN_Y3 <- val_upp/(1+val_upp)


#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

plot(cred_int$Prob, cred_int$Year)


ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
  geom_point(aes(size=UKRN)) +
  geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
  scale_size_manual(values=c(3,3)) +
  theme_classic()
```
Mean lambda for students in Non-UKRN university = 1.33    
Mean lambda for students in a UKRN university = 3.56  
Difference = 0.95  





### Learnt Open Science at Uni 

Bayesian Logistic regression for whether participants received teaching about open science or not (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    
Bayesian model for UKRN/Non-UKRN:


```{r Set_1 OS Learnt}

# Logistic multilevel model simulations

Index <- !is.na(data$os_learnt)
y <- data$os_learnt[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not


x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 2000
niter <- 4000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do not cross 0.  
2.5% = 0.14  
97.5% = 1.90  
So the interpretation is that students who attend a UKRN affiliated university are more likely to have learnt about open science.  
  
To see the magnitude of this difference. 
```{r OS Learnt effect}
ParDraws <- extract(fit)
 
 lambda_UKRN <- exp(ParDraws$mu + ParDraws$beta*1)
 lambda_NonUKRN <- exp(ParDraws$mu)
 plot(density(lambda_UKRN),col="blue")
 lines(density(lambda_NonUKRN),col="red")
 mean(lambda_UKRN > lambda_NonUKRN)
```
Mean lambda for students in Non-UKRN university = 0.17    
Mean lambda for students in a UKRN university = 0.48  
Difference = 0.986  
<!-- ? How to explain Lambda in the paper? --> 


### Can explain open science

Bayesian Logistic regression for whether participants can explain what open science is (yes/no). 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    
Bayesian model for UKRN/Non-UKRN:


```{r Set_1 OS Explain}

# Logistic multilevel model simulations

Index <- !is.na(data$os_explain)
y <- data$os_explain[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 2000
niter <- 4000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do cross 0.  
2.5% = -0.10  
97.5% = 0.63  
So the interpretation is that students who attend a UKRN affiliated university are not more likely to correctly explain open science.  
  
To see the magnitude of this difference. 
```{r OS Explain effect}
ParDraws <- extract(fit)
 
 lambda_UKRN <- exp(ParDraws$mu + ParDraws$beta*1)
 lambda_NonUKRN <- exp(ParDraws$mu)
 plot(density(lambda_UKRN),col="blue")
 lines(density(lambda_NonUKRN),col="red")
 mean(lambda_UKRN > lambda_NonUKRN)
```
Mean lambda for students in Non-UKRN university = 0.30    
Mean lambda for students in a UKRN university = 0.47  
Difference = 0.95  
<!-- ? How to explain Lambda in the paper? --> 


### Applicability

Bayesian Logistic regression for whether participants think that the issues discussed in the questionnaire are relevant to them. 
The explainer variables are:  
  -  Whether the participant was at a university that was affiliated with the UKRN
  -  whether the participant was in their first, second, placement of third year  
    
Bayesian model for UKRN/Non-UKRN:


```{r Set_1 Applicability}

# Logistic multilevel model simulations

Index <- !is.na(data$applicability)
y <- data$applicability[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 2000 #5000
niter <- 4000 #10 000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

```
The output shows that beta credibility intervals do cross 0.  
2.5% = -1.06  
97.5% = 0.30  
So the interpretation is that students who attend a UKRN affiliated university are not more likely to correctly explain open science.  
  
To see the magnitude of this difference. 
```{r Applicability effect}
ParDraws <- extract(fit)
 
 lambda_UKRN <- exp(ParDraws$mu + ParDraws$beta*1)
 lambda_NonUKRN <- exp(ParDraws$mu)
 plot(density(lambda_UKRN),col="blue")
 lines(density(lambda_NonUKRN),col="red")
 mean(lambda_UKRN > lambda_NonUKRN)
```
Mean lambda for students in Non-UKRN university = 13.57    
Mean lambda for students in a UKRN university = 13.38  
Difference = 0.46  
<!-- ? How to explain Lambda in the paper? --> 
