---
title: "Wave 3 Statistical Analyses"
output: pdf_document
author: Marta Topor & Bertil Wegmann
date: August 2024
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(rstan)
library(ggplot2)
```

# Hierarchical Bayesian Models Wave 1

This document runs the models used to analyse the main outcomes for Wave 1.   
The structure of the document follows the Analysis_Plans.txt file.   
The variables in the datasets are explained in Meta-Data.txt.  
<!-- ADD DETAILS The STAN files with the model formulas are...--> 
  

## Data Set 1 - Binary Categorical Outcomes
  
### Crisis aware

Bayesian Logistic regression for whether participants were aware of the reproducibility crisis or not (yes/no). 
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  
  
  
    
```{r Set_1 Crisis Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W1_Set1_AllData.csv", sep = "")) 

# Prepare all objects for the model

Index <- !is.na(data$crisis_aware)
y <- data$crisis_aware[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Crisis Aware Result}

print(fit)

```
  
**Number of participants in the analysis**    
  
**Total N** = `r length(data$ID) - sum(is.na(data$crisis_aware))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$crisis_aware[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$crisis_aware[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Final Year']))`  
  
  
The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `    
  
  
The interpretation is that students who attend a UKRN affiliated university are more likely to be aware of the reproducibility crisis in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  
  
  
```{r Crisis Aware effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

crisis_aware_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Crisis Aware plot print}

crisis_aware_plot + ggtitle("Pooled Probability for Crisis Awareness") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Learned about Open Science at Uni  

Bayesian Logistic regression for whether participants received teaching about open science or not (yes/no).  
The explainer variables are:   
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year 
* Interaction between the two variables above  
    

```{r Set_1 OS Learnt, include = FALSE}

Index <- !is.na(data$os_learnt)
y <- data$os_learnt[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not


x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```


```{r Set_1 OS Learnt result print}

print(fit)

```
  
**Number of participants in the analysis**    
  
  
**Total N** = `r length(data$ID) - sum(is.na(data$os_learnt))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$os_learnt[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$os_learnt[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$os_learnt[data$Current_Year == 'Year 1']))`   
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$os_learnt[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$os_learnt[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$os_learnt[data$Current_Year == 'Final Year']))`  
  
  
The output shows that all beta credibility intervals do cross 0. The results are non-significant.  


```{r OS Learnt effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

OS_learnt_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r OS Learnt plot print}

OS_learnt_plot + ggtitle("Pooled Probability for Learned About Open Science") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```
  
  
### Can explain open science  
  
Bayesian Logistic regression for whether participants can explain what open science is (yes/no).  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year  
* Interaction between the two variables above  
    


```{r Set_1 OS Explain, include = FALSE}

# Logistic multilevel model simulations

Index <- !is.na(data$os_explain)
y <- data$os_explain[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)
```


```{r Set_1 OS Explain result print}

print(fit)

``` 
  
**Number of participants in the analysis**    
  
**Total N** = `r length(data$ID) - sum(is.na(data$os_explain))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$os_explain[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$os_explain[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$os_explain[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$os_explain[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$os_explain[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$os_explain[data$Current_Year == 'Final Year']))`  
  
  
The output shows that all beta credibility intervals do cross 0. No significant results.  


```{r OS Explain effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

OS_explain_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r OS Explain plot print}

OS_explain_plot + ggtitle("Pooled Probability for Can Explain Open Science") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Applicability  

Bayesian Logistic regression for whether participants think that the issues discussed in the questionnaire are relevant to them (yes/no). 
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year  
* Interaction between the two variables above  
    

```{r Set_1 Applicability, include = FALSE}

# Logistic multilevel model simulations

Index <- !is.na(data$applicability)
y <- data$applicability[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000 #5000
niter <- 10000 #10 000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Set_1 Applicability result}

print(fit)

```
  
**Number of participants in the analysis**    
  
  
**Total N** = `r length(data$ID) - sum(is.na(data$applicability))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$applicability[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$applicability[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$applicability[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$applicability[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$applicability[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$applicability[data$Current_Year == 'Final Year']))`  
  
  
The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `    
  
  
The interpretation is that students who attend a UKRN affiliated university are more likely to think that the issues around open and reproducible research are applicable to their work in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  


```{r Set_1 Applicability effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

applicability_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Applicability plot print}

applicability_plot + ggtitle("Pooled Probability for Perceived Applicability of Issues") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```
 

## Data Set 2 - Truncated Poisson Regression  

### Awarweness Score Total  

Bayesian regression for how much awareness of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  
  

```{r Total Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W1_Set2_Awareness.csv", sep = "")) 

# Prepare all objects

y <- data$Awareness_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

#U = 8 #the upper truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Total Aware result}

print(fit)

```
  
**Number of participants in the analysis**   
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  
  
     
The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `   


The interpretation is that students who attend a UKRN affiliated university are more likely to be aware of the issues around open and reproducible research in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  
  
\textcolor{red}{
13 divergent transitions.  
}

```{r Set_2 Awareness effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

awareness_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Awareness plot print}

awareness_plot + ggtitle("Pooled Probability for the Awareness of Issues") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```
  
  

### Experience Score Total  

Bayesian regression for how much experience of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  

  
```{r Total Experience, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W1_Set2_Experience.csv", sep = "")) 

# Prepare all objects

y <- data$Experience_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

#U = 8 #the upper truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Total Experience result}

print(fit)

```
  
**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

The output shows that all beta credibility intervals cross 0.  

\textcolor{red}{2400 divergent transitions. In addition:  
-  There were 2 chains where the estimated Bayesian Fraction of Missing Information was low.  
-  The largest R-hat is 1.05, indicating chains have not mixed. Running the chains for more iterations may help.  
-  Effective Samples Size (ESS) is too low, indicating posterior means and medians may be unreliable.  
-  Effective Samples Size (ESS) is too low, indicating posterior variances and tail quantiles may be unreliable.  
}
  

```{r Set_2 experience effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

experience_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Experience plot print}

experience_plot + ggtitle("Pooled Probability for the Eperience with OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


## Data Set 2 - Linear Regression  

### Conceptual Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research. The scores are between -2 and 2 but will be changed by adding 2.001. This way the scale will be from 0 to 4.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  
  
  
```{r Concept Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W1_Set2_ConceptualPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Perception_Score_Mean <- data$Perception_Score_Total/16

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Perception_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Concept Perception result}

print(fit)

```

**Number of participants in the analysis**  

**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

The output shows that all beta credibility intervals cross 0.  

\textcolor{red}{46 divergent transitions.  
}

```{r Conceptual perception effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

concept_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r ConceptPerception plot print}

concept_plot + ggtitle("Pooled Probability for positive Conceptual Perceptions of OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Situational Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research. The scores are between -2 and 2 but will be changed by adding 2.001. This way the scale will be from 0 to 4.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year   
* Interaction between the two variables above  
  


```{r Situational Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W1_Set2_SituationalPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Knowledge_Score_Mean <- data$Knowledge_Score_Total/8

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Knowledge_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as DKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```


```{r Situational Perception result}

print(fit)

```

**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

The output shows that beta credibility intervals do not cross 0 only for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `   


The interpretation is that students who attend a UKRN affiliated university are more likely to have positive situational perceptions of open and reproducible practices in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  

```{r Situational perception effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(sort(ParDraws[["mu"]]))
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  sort(ParDraws[["beta1"]])
all_beta$beta2 <-  sort(ParDraws[["beta2"]])
all_beta$beta3 <-  sort(ParDraws[["beta3"]])

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y1 <- p_all[500] 
prob97.5_UKRN_Y1 <- p_all[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2 <- p_all[500]
prob97.5_UKRN_Y2 <- p_all[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y2.5 <- p_all[500]
prob97.5_UKRN_Y2.5 <- p_all[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_UKRN_Y3 <- p_all[500]
prob97.5_UKRN_Y3 <- p_all[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y1 <- p_all[500]
prob97.5_N_UKRN_Y1 <- p_all[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2 <- p_all[500]
prob97.5_N_UKRN_Y2 <- p_all[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 


prob2.5_N_UKRN_Y2.5 <- p_all[500]
prob97.5_N_UKRN_Y2.5 <- p_all[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

prob2.5_N_UKRN_Y3 <- p_all[500]
prob97.5_N_UKRN_Y3 <- p_all[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

situational_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_smooth(method=NULL, se=FALSE, fullrange=TRUE) +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r SituatinalPerception plot print}

situational_plot + ggtitle("Pooled Probability for positive Conceptual Perceptions of OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```