---
title: "Wave 3 Statistical Analyses"
output: pdf_document
author: Marta Topor & Bertil Wegmann
date: August 2024
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(rstan)
library(ggplot2)
set.seed(123)
```

# Hierarchical Bayesian Models Wave 3

This document runs the models used to analyse the main outcomes for Wave 3.   
The structure of the document follows the Analysis_Plans.txt file.   
The variables in the datasets are explained in Meta-Data.txt.  


## Data Set 1 - Binary Categorical Outcomes
  
### Crisis aware

Bayesian Logistic regression for whether participants were aware of the reproducibility crisis or not (yes/no). 
The explainer variables are:  
* Whether the participant was in their first, second, placement or third year  

  
    
```{r Set_1 Crisis Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W3_Set1_AllData.csv", sep = "")) 

# Prepare all objects for the model

Index <- !is.na(data$crisis_aware)
y <- data$crisis_aware[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Crisis Aware Result}

print(fit)

```
  
**Number of participants in the analysis**    
  
**Total N** = `r length(data$ID) - sum(is.na(data$crisis_aware))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$crisis_aware[data$Current_Year == 'Final Year']))`  
  
  
The output shows no significant results. 
  
  

```{r Crisis Aware effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X 
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y1 <- p_all_sorted[500] 
prob97.5_UKRN_Y1 <- p_all_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2 <- p_all_sorted[500]
prob97.5_UKRN_Y2 <- p_all_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y3 <- p_all_sorted[500]
prob97.5_UKRN_Y3 <- p_all_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y1 <- p_all_sorted[500]
prob97.5_N_UKRN_Y1 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y3 <- p_all_sorted[500]
prob97.5_N_UKRN_Y3 <- p_all_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

crisis_aware_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Crisis Aware plot print}

crisis_aware_plot + ggtitle("Pooled Probability for Crisis Awareness") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Learned about Open Science at Uni  

Bayesian Logistic regression for whether participants received teaching about open science or not (yes/no).  
The explainer variables are:   
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year 
* Interaction between the two variables above  
    

```{r Set_1 OS Learnt, include = FALSE}

Index <- !is.na(data$os_learnt)
y <- data$os_learnt[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as UKRN or not


x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)

print(fit)

output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```


```{r Set_1 OS Learnt result print}

print(fit)

```
  
**Number of participants in the analysis**    
  
  
**Total N** = `r length(data$ID) - sum(is.na(data$os_learnt))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$os_learnt[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$os_learnt[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$os_learnt[data$Current_Year == 'Year 1']))`   
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$os_learnt[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$os_learnt[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$os_learnt[data$Current_Year == 'Final Year']))`  
  
  
\textcolor{red}{ There were no errors here but the models took a long time to process and the result shows high Rhat values. The results also look quite strange with very large values for Beta 1 and Beta 2. There are conflicting findings in the output }

The output shows that beta credibility intervals do not cross 0 for Beta 2 but in the negative direction. This seems to suggest that likelihood of learning about open science is larger in earlier years of education at university  
2.5% = `r output_summary['beta2','2.5%'] `  
97.5% = `r output_summary['beta2','97.5%'] ` 

There is also a significant interaction for Beta 3 in the positive direction suggesting that the likelihood of learning about open science goes up with the year of study for UKRN universities.
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] ` 


```{r OS Learnt effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y1 <- p_all_sorted[500] 
prob97.5_UKRN_Y1 <- p_all_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2 <- p_all_sorted[500]
prob97.5_UKRN_Y2 <- p_all_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y3 <- p_all_sorted[500]
prob97.5_UKRN_Y3 <- p_all_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y1 <- p_all_sorted[500]
prob97.5_N_UKRN_Y1 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y3 <- p_all_sorted[500]
prob97.5_N_UKRN_Y3 <- p_all_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

OS_learnt_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r OS Learnt plot print}

OS_learnt_plot + ggtitle("Pooled Probability for Learned About Open Science") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```
  
  
### Can explain open science  
  
Bayesian Logistic regression for whether participants can explain what open science is (yes/no).  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year  
* Interaction between the two variables above  
    


```{r Set_1 OS Explain, include = FALSE}

# Logistic multilevel model simulations

Index <- !is.na(data$os_explain)
y <- data$os_explain[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)
```


```{r Set_1 OS Explain result print}

print(fit)

``` 
  
**Number of participants in the analysis**    
  
**Total N** = `r length(data$ID) - sum(is.na(data$os_explain))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$os_explain[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$os_explain[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$os_explain[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$os_explain[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$os_explain[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$os_explain[data$Current_Year == 'Final Year']))`  
  
  
The output shows that all beta credibility intervals do cross 0. No significant results.  

\textcolor{red}{ There were 19 divergent transitions after warmup }


```{r OS Explain effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y1 <- p_all_sorted[500] 
prob97.5_UKRN_Y1 <- p_all_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2 <- p_all_sorted[500]
prob97.5_UKRN_Y2 <- p_all_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y3 <- p_all_sorted[500]
prob97.5_UKRN_Y3 <- p_all_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y1 <- p_all_sorted[500]
prob97.5_N_UKRN_Y1 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y3 <- p_all_sorted[500]
prob97.5_N_UKRN_Y3 <- p_all_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

OS_explain_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r OS Explain plot print}

OS_explain_plot + ggtitle("Pooled Probability for Can Explain Open Science") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Applicability  

Bayesian Logistic regression for whether participants think that the issues discussed in the questionnaire are relevant to them (yes/no). 
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement of third year  
* Interaction between the two variables above  
    

```{r Set_1 Applicability, include = FALSE}

# Logistic multilevel model simulations

Index <- !is.na(data$applicability)
y <- data$applicability[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN[Index]=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year[Index]
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000 #5000
niter <- 10000 #10 000
fit <- stan(file="STORM_logistic_fullmodel.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Set_1 Applicability result}

print(fit)

```
  
**Number of participants in the analysis**    
  
  
**Total N** = `r length(data$ID) - sum(is.na(data$applicability))`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN']) - sum(is.na(data$applicability[data$UKRN == 'UKRN']))`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN']) - sum(is.na(data$applicability[data$UKRN == 'Non-UKRN']))`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1']) - sum(is.na(data$applicability[data$Current_Year == 'Year 1']))`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2']) - sum(is.na(data$applicability[data$Current_Year == 'Year 2']))`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year']) - sum(is.na(data$applicability[data$Current_Year == 'Placement Year']))`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year']) - sum(is.na(data$applicability[data$Current_Year == 'Final Year']))`  
  
  
The output shows that all beta credibility intervals do cross 0. No significant results.  

\textcolor{red}{ There were 800 divergent transitions after warmup }


```{r Set_1 Applicability effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)


prob2.5_UKRN_Y1 <- p_all_sorted[500] 
prob97.5_UKRN_Y1 <- p_all_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2 <- p_all_sorted[500]
prob97.5_UKRN_Y2 <- p_all_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_UKRN_Y3 <- p_all_sorted[500]
prob97.5_UKRN_Y3 <- p_all_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y1 <- p_all_sorted[500]
prob97.5_N_UKRN_Y1 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2 <- p_all_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y2.5 <- p_all_sorted[500]
prob97.5_N_UKRN_Y2.5 <- p_all_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

matrix1 <- all_beta %*% X
matrix2 <- matrix1 + mu_all

p_all <- exp(matrix2)/(1+exp(matrix2)) 

p_all_sorted <- sort(p_all)

prob2.5_N_UKRN_Y3 <- p_all_sorted[500]
prob97.5_N_UKRN_Y3 <- p_all_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("Prob", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

applicability_plot <- ggplot(cred_int, aes(x=Year, y=Prob, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Applicability plot print}

applicability_plot + ggtitle("Pooled Probability for Perceived Applicability of Issues") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```
 

## Data Set 2 - Truncated Poisson Regression  

### Awarweness Score Total  

Bayesian regression for how much awareness of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  
  

```{r Total Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_Awareness.csv", sep = "")) 

# Prepare all objects

y <- data$Awareness_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

#U = 8 #the upper truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- rstan::extract(fit)

```

```{r Total Aware result}

print(fit)

```
  
**Number of participants in the analysis**   
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  
  
`r knitr::kable(table(data$Awareness_Score_Total))`
     
The output shows that beta credibility intervals do not cross 0 for Beta1 in the negative direction.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `  
  
The interpretation is that awareness of open and reproducible research is significantly more likely in students who are in non-UKRN universities.

The output shows that beta credibility intervals do not cross 0 for the interaction term.  
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `   

The interpretation is that students who attend a UKRN affiliated university are more likely to be aware of the issues around open and reproducible research in the later years of education. For students who attend a non-URKN affiliated university, there is no difference.  
  
\textcolor{red}{ There were 4 divergent transitions after warmup. }

```{r Set_2 Awareness effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y1 <- Exp_val_sorted[500] 
prob97.5_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_UKRN_Y3 <- Exp_val_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)


prob2.5_N_UKRN_Y1 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y3 <- Exp_val_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("ExpectedValue", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

awareness_plot <- ggplot(cred_int, aes(x=Year, y=ExpectedValue, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Awareness plot print}

awareness_plot + ggtitle("Expected Value for the Awareness of Issues") +
  xlab("Current Year at University") + ylab("Expected Value") +
  theme(plot.title = element_text(hjust = 0.5))

```
  
  

### Experience Score Total  

Bayesian regression for how much experience of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  

  
```{r Total Experience, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_Experience.csv", sep = "")) 

# Prepare all objects

y <- data$Experience_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x

#U = 8 #the upper truncation at value U

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- rstan::extract(fit)

```

```{r Total Experience result}

print(fit)

```
  
**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

`r knitr::kable(table(data$Experience_Score_Total))`

The output shows that all beta credibility intervals cross 0.  

\textcolor{red}{ There were 4 divergent transitions after warmup. }
  

```{r Set_2 experience effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y1 <- Exp_val_sorted[500] 
prob97.5_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_UKRN_Y3 <- Exp_val_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y1 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

lambda <- exp( mu_all + all_beta %*% X )
int_vec <- 0:8
Exp_val <- matrix(0,length(lambda),1)
for (ii in 1:length(lambda)){
  lambda_curr <- lambda[ii]
  probs_curr <- dpois(int_vec,lambda_curr)
  Exp_val[ii] <- sum(int_vec*probs_curr)/sum(probs_curr)
}

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y3 <- Exp_val_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("ExpectedValue", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

experience_plot <- ggplot(cred_int, aes(x=Year, y=ExpectedValue, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r Experience plot print}

experience_plot + ggtitle("Pooled Probability for the Eperience with OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


## Data Set 2 - Linear Regression  

### Conceptual Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research.   
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year  
* Interaction between the two variables above  
  
  
```{r Concept Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_ConceptualPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Perception_Score_Mean <- data$Perception_Score_Total/16

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Perception_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr.stan",data=data2, warmup=warmup,iter=niter,chains=4)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- rstan::extract(fit)

```

```{r Concept Perception result}

print(fit)

```

**Number of participants in the analysis**  

**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

The output shows that all beta credibility intervals cross 0.  

\textcolor{red}{ 6 divergent transitions. }


```{r Conceptual perception effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

sigma_all <- as.data.frame(ParDraws[["sigma"]])
colnames(sigma_all) <- 'sigma'
sigma_all <- as.matrix(sigma_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y1 <- Exp_val_sorted[500] 
prob97.5_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_UKRN_Y3 <- Exp_val_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y1 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y3 <- Exp_val_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("ExpectedValue", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

concept_plot <- ggplot(cred_int, aes(x=Year, y=ExpectedValue, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r ConceptPerception plot print}

concept_plot + ggtitle("Expected Value for positive Conceptual Perceptions of OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```


### Situational Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research.   
The explainer variables are:  
* Whether the participant was at a university that was affiliated with the UKRN  
* Whether the participant was in their first, second, placement or third year   
* Interaction between the two variables above  
  


```{r Situational Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_SituationalPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Knowledge_Score_Mean <- data$Knowledge_Score_Total/8

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Knowledge_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$UKRN=="UKRN",1,0) # mark universities as UKRN or not

x <- vector(length =N)
tmp <- data$Current_Year
x[tmp == 'Year 1'] <- 1
x[tmp == 'Year 2'] <- 2
x[tmp == 'Placement Year'] <- 2.5
x[tmp == 'Final Year'] <- 3

interact <- D*x


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, x=x, interact=interact)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr.stan",data=data2, warmup=warmup,iter=niter,chains=4)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- rstan::extract(fit)

```


```{r Situational Perception result}

print(fit)

```

**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**UKRN N** = `r length(data$UKRN[data$UKRN == 'UKRN'])`  
**Non-UKRN N** = `r length(data$UKRN[data$UKRN == 'Non-UKRN'])`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**Placement Year N** = `r length(data$Current_Year[data$Current_Year == 'Placement Year'])`  
**Year 4 N** = `r length(data$Current_Year[data$Current_Year == 'Final Year'])`  

The output shows that all beta credibility intervals cross 0.  

\textcolor{red}{ 11 divergent transitions. }

```{r Situational perception effect, include = FALSE}
#Make plots for UKRN vs Non-UKRN - how does the probability differ for the different years 
# y axis would be probability and x axis would be years 

#probability at 2.5% and 97.5% for UKRN and NON-UKRN per year

#Prob = exp(mu + (Bj * X)) / (1 + exp( mu + (Bj * X)))
#Bj = beta1j  beta2j  beta3j 
#X = D * x * (D*x)   


#sort the draws 
# make mu into a matrix with just one column
mu_all <- as.data.frame(ParDraws[["mu"]])
colnames(mu_all) <- 'mu'
mu_all <- as.matrix(mu_all)

#make the betas into a matrix with 20 000 rows for draws and 3 columns for betas
all_beta <- as.data.frame(matrix(data = NA, nrow = 20000, ncol =3))
colnames(all_beta) <- c('beta1', 'beta2', 'beta3')
all_beta$beta1 <-  ParDraws[["beta1"]]
all_beta$beta2 <-  ParDraws[["beta2"]]
all_beta$beta3 <-  ParDraws[["beta3"]]

all_beta <- as.matrix(all_beta)

#Calculation steps:

#1. all_beta should be multiplied by an X matrix with 3 rows and 1 column transpose [D x D*x] (the result will be a matrix with 20 000 rows and 1 column)
#the X matrix will be different for each combination of UKRN status and Current year, D=UKRN status, x = current year

#2. Add the matrix for mu with 20 000 rows and 1 column 

#3. p <- exp(resulting_matrix)/(1+exp(resulting_matrix)) # this will be the final probability matrix and then you can take out the quantiles


#-----------UKRN VALUES -----------------------
#Probability for UKRN Year 1 
prob2.5_UKRN_Y1 <- 0 
prob97.5_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <-  c(1, 1, (1*1)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y1 <- Exp_val_sorted[500] 
prob97.5_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2 at 2.5% and 97.5%
prob2.5_UKRN_Y2 <- 0
prob97.5_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2, (1*2)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_UKRN_Y2.5 <- 0
prob97.5_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 2.5, (1*2.5)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for UKRN Year 3 at 2.5% and 97.5%
prob2.5_UKRN_Y3 <- 0
prob97.5_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(1, 3, (1*3)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_UKRN_Y3 <- Exp_val_sorted[19500]


#-------------NON-UKRN VALUES----------------------

#Probability for non-UKRN Year 1 at 2.5% and 97.5%
prob2.5_N_UKRN_Y1 <- 0
prob97.5_N_UKRN_Y1 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 1, (0*1)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y1 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y1 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2 <- 0
prob97.5_N_UKRN_Y2 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 <- c(0, 2, (0*2)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 2.5 at 2.5% and 97.5%
prob2.5_N_UKRN_Y2.5 <- 0
prob97.5_N_UKRN_Y2.5 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 2.5, (0*2.5)) # [D x D*x] 
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y2.5 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y2.5 <- Exp_val_sorted[19500]


#Probability for non-UKRN Year 3 at 2.5% and 97.5%
prob2.5_N_UKRN_Y3 <- 0
prob97.5_N_UKRN_Y3 <- 0
X <- as.data.frame(matrix(data = NA, nrow =3, ncol = 1))
X$V1 = c(0, 3, (0*3)) # [D x D*x]
X <- as.matrix(X)

mu_y <- mu_all + all_beta %*% X
alpha <- (-2 - mu_y)/sigma_all 
beta <- (2 - mu_y)/sigma_all

Z <- pnorm(beta) - pnorm(alpha)

diff <- dnorm(alpha) - dnorm(beta)

Exp_val <- mu_y + diff*sigma_all/Z

Exp_val_sorted <- sort(Exp_val)

prob2.5_N_UKRN_Y3 <- Exp_val_sorted[500]
prob97.5_N_UKRN_Y3 <- Exp_val_sorted[19500]




#Make a data frame to plot
cred_int <- data.frame(Prob = c(prob2.5_UKRN_Y1, prob97.5_UKRN_Y1, prob2.5_UKRN_Y2, prob97.5_UKRN_Y2, prob2.5_UKRN_Y2.5, prob97.5_UKRN_Y2.5, prob2.5_UKRN_Y3, prob97.5_UKRN_Y3, prob2.5_N_UKRN_Y1, prob97.5_N_UKRN_Y1, prob2.5_N_UKRN_Y2, prob97.5_N_UKRN_Y2, prob2.5_N_UKRN_Y2.5, prob97.5_N_UKRN_Y2.5, prob2.5_N_UKRN_Y3, prob97.5_N_UKRN_Y3),
                 Year = c(1, 1, 2, 2, 2.5, 2.5, 3, 3, 1, 1, 2, 2, 2.5, 2.5, 3, 3),
                 UKRN= c('UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN', 'Non-UKRN'), 
                 Percent = c(2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5, 2.5, 97.5))

colnames(cred_int) <- c("ExpectedValue", "Year", "UKRN", "Percent")
cred_int$Percent <- as.factor(cred_int$Percent)

situational_plot <- ggplot(cred_int, aes(x=Year, y=ExpectedValue, shape = Percent, color = UKRN)) +
                      geom_point(aes(size=UKRN)) +
                      geom_line() +
                      scale_size_manual(values=c(3,3)) +
                      theme_classic()
```

```{r SituatinalPerception plot print}

situational_plot + ggtitle("Expected Value for positive Conceptual Perceptions of OS Practices") +
  xlab("Current Year at University") + ylab("Probability") +
  theme(plot.title = element_text(hjust = 0.5))

```




## Dataset 2 - Beta Bernoulli Model 

### For the most common category in the Awareness variable  
  
The categories are: * Replication * Open Research Materials * Open Educational
Materials * Open Access Journals * Open Data * Power Analysis * Preregistration
* Preprint  

```{r beta-bernoulli for categories awareness}  

data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_Awareness.csv", sep = ""))

#A vector with the number of yeses
yes <- c(sum(data$Awareness_Replication), sum(data$Awareness_Materials),
sum(data$Awareness_Education), sum(data$Awareness_Access),
sum(data$Awareness_Data), sum(data$Awareness_Power),
sum(data$Awareness_Preregistration), sum(data$Awareness_Preprint))

#A vector with the number of nos
no <- c(sum(data$Awareness_Replication == 0), sum(data$Awareness_Materials ==0),
sum(data$Awareness_Education ==0), sum(data$Awareness_Access ==0),
sum(data$Awareness_Data ==0), sum(data$Awareness_Power ==0),
sum(data$Awareness_Preregistration ==0), sum(data$Awareness_Preprint ==0))


highest_pi_1 <- matrix(0, 1e6, 1)
highest_pi_2 <- matrix(0, 1e6, 1)
highest_pi_3 <- matrix(0, 1e6, 1)
highest_pi_4 <- matrix(0, 1e6, 1)
highest_pi_5 <- matrix(0, 1e6, 1)
highest_pi_6 <- matrix(0, 1e6, 1)
highest_pi_7 <- matrix(0, 1e6, 1)
highest_pi_8 <- matrix(0, 1e6, 1)

pi_1 <- rbeta(1e6, 1+yes[1], 1+no[1])
pi_2 <- rbeta(1e6, 1+yes[2], 1+no[2])
pi_3 <- rbeta(1e6, 1+yes[3], 1+no[3])
pi_4 <- rbeta(1e6, 1+yes[4], 1+no[4])
pi_5 <- rbeta(1e6, 1+yes[5], 1+no[5])
pi_6 <- rbeta(1e6, 1+yes[6], 1+no[6])
pi_7 <- rbeta(1e6, 1+yes[7], 1+no[7])
pi_8 <- rbeta(1e6, 1+yes[8], 1+no[8])

plot(density(pi_1), xlim = c(0,1))
lines(density(pi_2))
lines(density(pi_3))
lines(density(pi_4))
lines(density(pi_5))
lines(density(pi_6))
lines(density(pi_7))
lines(density(pi_8))

#can remove the forloop and make one big matrix with 8 columns instead 

for (jj in 1:1e6){ 
  pi_1 <- rbeta(1, 1+yes[1], 1+no[1])
  pi_2 <- rbeta(1, 1+yes[2], 1+no[2]) 
  pi_3 <- rbeta(1, 1+yes[3], 1+no[3]) 
  pi_4 <- rbeta(1, 1+yes[4], 1+no[4]) 
  pi_5 <- rbeta(1, 1+yes[5], 1+no[5])
  pi_6 <- rbeta(1, 1+yes[6], 1+no[6]) 
  pi_7 <- rbeta(1, 1+yes[7], 1+no[7])
  pi_8 <- rbeta(1, 1+yes[8], 1+no[8])
                                                             
if (pi_1 > pi_2 & pi_1 > pi_3 & pi_1 > pi_4 & pi_1 > pi_5 & pi_1 > pi_6 & pi_1 > pi_7 & pi_1 > pi_8) { 
  highest_pi_1[jj] <- 1 }
  
if (pi_2 > pi_1 & pi_2 > pi_3 & pi_2 > pi_4 & pi_2 > pi_5 & pi_2 > pi_6 & pi_2 > pi_7 & pi_2 > pi_8) { 
  highest_pi_2[jj] <- 1 }
  
if (pi_3 > pi_2 & pi_3 > pi_1 & pi_3 > pi_4 & pi_3 > pi_5 & pi_3 > pi_6 & pi_3 > pi_7 & pi_3 > pi_8) { 
  highest_pi_3[jj] <- 1 }  
  
if (pi_4 > pi_2 & pi_4 > pi_3 & pi_4 > pi_1 & pi_4 > pi_5 & pi_4 > pi_6 & pi_4 > pi_7 & pi_4 > pi_8) { 
  highest_pi_4[jj] <- 1 }
 
if (pi_5 > pi_2 & pi_5 > pi_3 & pi_5 > pi_4 & pi_5 > pi_1 & pi_5 > pi_6 & pi_5 > pi_7 & pi_5 > pi_8) { 
  highest_pi_5[jj] <- 1 } 

if (pi_6 > pi_2 & pi_6 > pi_3 & pi_6 > pi_4 & pi_6 > pi_5 & pi_6 > pi_1 & pi_6 > pi_7 & pi_6 > pi_8) { 
  highest_pi_1[jj] <- 1 }  
  
if (pi_7 > pi_2 & pi_7 > pi_3 & pi_7 > pi_4 & pi_7 > pi_5 & pi_7 > pi_6 & pi_7 > pi_1 & pi_7 > pi_8) { 
  highest_pi_7[jj] <- 1 }
  
  if (pi_8 > pi_2 & pi_8 > pi_3 & pi_8 > pi_4 & pi_8 > pi_5 & pi_8 > pi_6 & pi_8 > pi_7 & pi_8 > pi_1) { 
  highest_pi_8[jj] <- 1 }
}

probs_Awareness <- data.frame(row.names = c('Replication', 'Open Research Materials', 'Open Educational
Materials', 'Open Access Journals', 'Open Data', 'Power Analysis', 'Preregistration', 'Preprint'))

probs_Awareness$Probability <- 0


probs_Awareness$Probability[1] <- mean(round(highest_pi_1, 2))
probs_Awareness$Probability[2] <- mean(round(highest_pi_2, 2))
probs_Awareness$Probability[3] <- mean(round(highest_pi_3, 2))
probs_Awareness$Probability[4] <- mean(round(highest_pi_4, 2))
probs_Awareness$Probability[5] <- mean(round(highest_pi_5, 2))
probs_Awareness$Probability[6] <- mean(round(highest_pi_6, 2))
probs_Awareness$Probability[7] <- mean(round(highest_pi_7, 2))
probs_Awareness$Probability[8] <- mean(round(highest_pi_8, 2))

probs_Awareness

#Prob that pi_1 is the highest proportion of YES among categories
```

`probs_Awareness` 



### For the most common category in the Experience variable  
  
The categories are: * Replication * Open Research Materials * Open Educational
Materials * Open Access Journals * Open Data * Power Analysis * Preregistration
* Preprint  

```{r beta-bernoulli for categories experience}  

data <- read.csv(paste(project_path, "/cleaned_data/W3_Set2_Experience.csv", sep = ""))

#A vector with the number of yeses
yes <- c(sum(data$Experience_Replication), sum(data$Experience_Materials),
sum(data$Experience_Education), sum(data$Experience_Access),
sum(data$Experience_Data), sum(data$Experience_Power),
sum(data$Experience_Preregistration), sum(data$Experience_Preprint))

#A vector with the number of nos
no <- c(sum(data$Experience_Replication == 0), sum(data$Experience_Materials ==0),
sum(data$Experience_Education ==0), sum(data$Experience_Access ==0),
sum(data$Experience_Data ==0), sum(data$Experience_Power ==0),
sum(data$Experience_Preregistration ==0), sum(data$Experience_Preprint ==0))


highest_pi_1 <- matrix(0, 1e6, 1)
highest_pi_2 <- matrix(0, 1e6, 1)
highest_pi_3 <- matrix(0, 1e6, 1)
highest_pi_4 <- matrix(0, 1e6, 1)
highest_pi_5 <- matrix(0, 1e6, 1)
highest_pi_6 <- matrix(0, 1e6, 1)
highest_pi_7 <- matrix(0, 1e6, 1)
highest_pi_8 <- matrix(0, 1e6, 1)

pi_1 <- rbeta(1e6, 1+yes[1], 1+no[1])
pi_2 <- rbeta(1e6, 1+yes[2], 1+no[2])
pi_3 <- rbeta(1e6, 1+yes[3], 1+no[3])
pi_4 <- rbeta(1e6, 1+yes[4], 1+no[4])
pi_5 <- rbeta(1e6, 1+yes[5], 1+no[5])
pi_6 <- rbeta(1e6, 1+yes[6], 1+no[6])
pi_7 <- rbeta(1e6, 1+yes[7], 1+no[7])
pi_8 <- rbeta(1e6, 1+yes[8], 1+no[8])

plot(density(pi_1), xlim = c(0,1))
lines(density(pi_2))
lines(density(pi_3))
lines(density(pi_4))
lines(density(pi_5))
lines(density(pi_6))
lines(density(pi_7))
lines(density(pi_8))

#can remove the forloop and make one big matrix with 8 columns instead 

for (jj in 1:1e6){ 
  pi_1 <- rbeta(1, 1+yes[1], 1+no[1])
  pi_2 <- rbeta(1, 1+yes[2], 1+no[2]) 
  pi_3 <- rbeta(1, 1+yes[3], 1+no[3]) 
  pi_4 <- rbeta(1, 1+yes[4], 1+no[4]) 
  pi_5 <- rbeta(1, 1+yes[5], 1+no[5])
  pi_6 <- rbeta(1, 1+yes[6], 1+no[6]) 
  pi_7 <- rbeta(1, 1+yes[7], 1+no[7])
  pi_8 <- rbeta(1, 1+yes[8], 1+no[8])
                                                             
if (pi_1 > pi_2 & pi_1 > pi_3 & pi_1 > pi_4 & pi_1 > pi_5 & pi_1 > pi_6 & pi_1 > pi_7 & pi_1 > pi_8) { 
  highest_pi_1[jj] <- 1 }
  
if (pi_2 > pi_1 & pi_2 > pi_3 & pi_2 > pi_4 & pi_2 > pi_5 & pi_2 > pi_6 & pi_2 > pi_7 & pi_2 > pi_8) { 
  highest_pi_2[jj] <- 1 }
  
if (pi_3 > pi_2 & pi_3 > pi_1 & pi_3 > pi_4 & pi_3 > pi_5 & pi_3 > pi_6 & pi_3 > pi_7 & pi_3 > pi_8) { 
  highest_pi_3[jj] <- 1 }  
  
if (pi_4 > pi_2 & pi_4 > pi_3 & pi_4 > pi_1 & pi_4 > pi_5 & pi_4 > pi_6 & pi_4 > pi_7 & pi_4 > pi_8) { 
  highest_pi_4[jj] <- 1 }
 
if (pi_5 > pi_2 & pi_5 > pi_3 & pi_5 > pi_4 & pi_5 > pi_1 & pi_5 > pi_6 & pi_5 > pi_7 & pi_5 > pi_8) { 
  highest_pi_5[jj] <- 1 } 

if (pi_6 > pi_2 & pi_6 > pi_3 & pi_6 > pi_4 & pi_6 > pi_5 & pi_6 > pi_1 & pi_6 > pi_7 & pi_6 > pi_8) { 
  highest_pi_1[jj] <- 1 }  
  
if (pi_7 > pi_2 & pi_7 > pi_3 & pi_7 > pi_4 & pi_7 > pi_5 & pi_7 > pi_6 & pi_7 > pi_1 & pi_7 > pi_8) { 
  highest_pi_7[jj] <- 1 }
  
  if (pi_8 > pi_2 & pi_8 > pi_3 & pi_8 > pi_4 & pi_8 > pi_5 & pi_8 > pi_6 & pi_8 > pi_7 & pi_8 > pi_1) { 
  highest_pi_8[jj] <- 1 }
}

probs_Experience <- data.frame(row.names = c('Replication', 'Open Research Materials', 'Open Educational
Materials', 'Open Access Journals', 'Open Data', 'Power Analysis', 'Preregistration', 'Preprint'))

probs_Experience$Probability <- 0


probs_Experience$Probability[1] <- mean(round(highest_pi_1, 2))
probs_Experience$Probability[2] <- mean(round(highest_pi_2, 2))
probs_Experience$Probability[3] <- mean(round(highest_pi_3, 2))
probs_Experience$Probability[4] <- mean(round(highest_pi_4, 2))
probs_Experience$Probability[5] <- mean(round(highest_pi_5, 2))
probs_Experience$Probability[6] <- mean(round(highest_pi_6, 2))
probs_Experience$Probability[7] <- mean(round(highest_pi_7, 2))
probs_Experience$Probability[8] <- mean(round(highest_pi_8, 2))

probs_Experience

#Prob that pi_1 is the highest proportion of YES among categories
```

`probs_Experience` 