---
title: "All Waves Statistical Analyses"
output: pdf_document
author: Marta Topor & Bertil Wegmann
date: January 2025
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(rstan) # version 2.26.23 and 2.26.28 for StanHeaders
library(ggplot2)
set.seed(123)
```

# Hierarchical Bayesian Models Cross-Waves analysis

This document runs the models used to analyse the over time changes in perceptions, awareness and experience of open science practices.   
The structure of the document follows the Analysis_Plans.txt file.   
The variables in the datasets are explained in Meta-Data.txt.  
<!-- ADD DETAILS The STAN files with the model formulas are...--> 

## Data Set 1 - Binary Categorical Outcomes
  
### Crisis aware

Bayesian Logistic regression for whether participants were aware of the reproducibility crisis or not (yes/no). 
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022 

  
    
```{r Set_1 Crisis Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/all_Set1_AllData.csv", sep = "")) 

# Prepare all objects for the model

Index <- !is.na(data$crisis_aware)
y <- data$crisis_aware[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0)# mark student who is in the second year as 1
D <- D[Index]
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D1 <- D1[Index]
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1
D2 <- D2[Index]

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Crisis Aware Result}

print(fit)

```
  

### Learnt about Open Science

Bayesian Logistic regression for whether participants learnt about open science during their studies or not (yes/no). 
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022   
  
  
```{r Set_1 OS_Learnt, include = FALSE}

# Prepare all objects for the model

Index <- !is.na(data$os_learnt)
y <- data$os_learnt[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0)# mark student who is in the second year as 1
D <- D[Index]
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D1 <- D1[Index]
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1
D2 <- D2[Index]

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r OS_Learnt Result}

print(fit)

```


### Can Explain Open Science

Bayesian Logistic regression for whether participants can explain open science or not (yes/no). 
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022   
  
  
```{r Set_1 OS_Explain, include = FALSE}

# Prepare all objects for the model

Index <- !is.na(data$os_explain)
y <- data$os_explain[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0)# mark student who is in the second year as 1
D <- D[Index]
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D1 <- D1[Index]
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1
D2 <- D2[Index]

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r OS_Explain Result}

print(fit)

```
### Applicability  

Bayesian Logistic regression for whether participants think that the issues discussed in the questionnaire are relevant to them (yes/no). 
The explainer variables are: 
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022   
  
  
```{r Set_1 applicability, include = FALSE}

# Prepare all objects for the model

Index <- !is.na(data$applicability)
y <- data$applicability[Index]
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni[Index]) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0)# mark student who is in the second year as 1
D <- D[Index]
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D1 <- D1[Index]
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1
D2 <- D2[Index]

# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_logistic_fullmodel_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)



output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r applicability Result}

print(fit)

```





## Data Set 2 - Truncated Poisson Regression  

### Awarweness Score Total  

Bayesian regression for how much awareness of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022 
  

```{r Total Aware, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/all_Set2_Awareness.csv", sep = "")) 

# Prepare all objects
y <- data$Awareness_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0) # mark student who is in the second year as 1
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1



# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Total Aware result}

print(fit)

```
  
**Number of participants in the analysis**   
  
**Total N** = `r length(data$ID)`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**2020 N** = `r length(data$timepoint[data$timepoint == 1])`   
**2021 N** = `r length(data$timepoint[data$timepoint == 2])`   
**2022 N** = `r length(data$timepoint[data$timepoint == 3])`  
  
`r knitr::kable(table(data$Awareness_Score_Total))`  
  
     
The output shows that beta credibility intervals are significant for Beta 1.    
2.5% = `r output_summary['beta1','2.5%'] `  
97.5% = `r output_summary['beta1','97.5%'] `   
  
The interpretation is that students across all waves, who were in their second year of study were more likely to have higher awareness of open science practices compared to students in the first year of study.  
    
     
The output shows that beta credibility intervals are significant for Beta 3.    
2.5% = `r output_summary['beta3','2.5%'] `  
97.5% = `r output_summary['beta3','97.5%'] `  


The interpretation is that students who answered the survey in 2022 were significantly more likely to have higher awareness of open science practices compared to students who answered the survey in 2020.  
  
\textcolor{red}{177 divergent transitions.}  
  
    
    
  

### Experience Score Total  

Bayesian regression for how much experience of open and reproducible research the students had - scores range from 0 to 8.  
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022  

  
```{r Total Experience, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/all_Set2_Experience.csv", sep = "")) 

# Prepare all objects

y <- data$Experience_Score_Total
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0) # mark student who is in the second year as 1
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1



# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncPoisson_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Total Experience result}

print(fit)

```
  
**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**2020 N** = `r length(data$timepoint[data$timepoint == 1])`   
**2021 N** = `r length(data$timepoint[data$timepoint == 2])`   
**2022 N** = `r length(data$timepoint[data$timepoint == 3])`  
 

`r knitr::kable(table(data$Experience_Score_Total))`

The output shows that beta credibility intervals are significant for Beta 1.    
2.5% = `r output_summary['beta1','2.5%'] `  
97.5% = `r output_summary['beta1','97.5%'] `   
  
The interpretation is that students across all waves, who were in their second year of study were more likely to have higher experience of open science practices compared to students in the first year of study.  
    
     
The output shows that beta credibility intervals are significant for Beta 2 in the negative direction.    
2.5% = `r output_summary['beta2','2.5%'] `  
97.5% = `r output_summary['beta2','97.5%'] `  


The interpretation is that students who answered the survey in 2020 were significantly more likely to have higher experience of open science practices compared to students who answered the survey in 2022.      
  
  
 
  
  
## Data Set 2 - Linear Regression  

### Conceptual Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research. The scores are between -2 and 2 but will be changed by adding 2.001. This way the scale will be from 0 to 4.  
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022   
  
  
```{r Concept Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/all_Set2_ConceptualPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Perception_Score_Mean <- data$Perception_Score_Total/16

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Perception_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0) # mark student who is in the second year as 1
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```

```{r Concept Perception result}

print(fit)

```

**Number of participants in the analysis**  

**Total N** = `r length(data$ID)`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**2020 N** = `r length(data$timepoint[data$timepoint == 1])`   
**2021 N** = `r length(data$timepoint[data$timepoint == 2])`   
**2022 N** = `r length(data$timepoint[data$timepoint == 3])`   

The output shows that all beta credibility intervals cross 0.  




### Situational Perception Score  

Bayesian regression for how positive are students perceptions of open and reproducible research. The scores are between -2 and 2 but will be changed by adding 2.001. This way the scale will be from 0 to 4.  
The explainer variables are:  
* Whether the participant was in their first or second year of study 
* The year the survey was conducted - 2020, 2021 and 2022   
  


```{r Situational Perception, include = FALSE}

#Set the path for the Wave 1 files

project_path <- gsub("/stats","", getwd())

#Read the data
data <- read.csv(paste(project_path, "/cleaned_data/all_Set2_SituationalPerception.csv", sep = "")) 

#fix the mean because it's not calculated correctly - keep limits -2 and 2
data$Knowledge_Score_Mean <- data$Knowledge_Score_Total/8

#in Stan code set the limits as L = -2.001 and U = 2.001


# Logistic multilevel model simulations

y <- data$Knowledge_Score_Mean
N <- length(y) # The number of observations

IDuni <- as.factor(data$Uni) #list the UNI for each participant
tmp <- sort(unique(IDuni)) #make a list of the unique UNIs

ll <- vector(length=N)

for (ii in 1:N){
  index2 <- IDuni[ii]==tmp
  ll[ii] <- which(index2 == TRUE) #mark which UNI per participant by factor and not the UNI name
}

L <- length(unique(ll)) # number of universities

D <- ifelse(data$Current_Year=="Year 2",1,0) # mark student who is in the second year as 1
D1 <- ifelse(data$timepoint == 2 ,1,0) # mark wave 2 (2021) as 1
D2 <- ifelse(data$timepoint == 3 ,1,0) # mark wave 3 (2022) as 1


# Estimate logistic multilevel model
data2 <- list(N=N, L=L, y=y, ll=ll, D=D, D1=D1, D2=D2)
warmup <- 5000
niter <- 10000
fit <- stan(file="STORM_truncRegr_allwaves.stan",data=data2, warmup=warmup,iter=niter,chains=4, cores=4, refresh=10)


output_summary <- summary(fit)
output_summary <- as.data.frame(output_summary[["summary"]])

ParDraws <- extract(fit)

```


```{r Situational Perception result}

print(fit)

```

**Number of participants in the analysis**  
  
**Total N** = `r length(data$ID)`  
**Year 1 N** = `r length(data$Current_Year[data$Current_Year == 'Year 1'])`  
**Year 2 N** = `r length(data$Current_Year[data$Current_Year == 'Year 2'])`  
**2020 N** = `r length(data$timepoint[data$timepoint == 1])`   
**2021 N** = `r length(data$timepoint[data$timepoint == 2])`   
**2022 N** = `r length(data$timepoint[data$timepoint == 3])`  

The output shows that beta credibility intervals do not cross 0 only for the Beta 1.  
2.5% = `r output_summary['beta1','2.5%'] `  
97.5% = `r output_summary['beta1','97.5%'] `   


The interpretation is that students across all waves, who were in their second year of study were more likely to have more positive situational perceptions of open science practices compared to students in the first year of study.   


### Descriptives


```{r descriptives}
#Read the data 

data <- read.csv(paste(project_path, "/cleaned_data/all_Set1_AllData.csv", sep = "")) 

crisis_aware_w1y1 <- sum(data$crisis_aware[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
crisis_aware_w1y2 <- sum(data$crisis_aware[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
crisis_aware_w2y1 <- sum(data$crisis_aware[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
crisis_aware_w2y2 <- sum(data$crisis_aware[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
crisis_aware_w3y1 <- sum(data$crisis_aware[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
crisis_aware_w3y2 <- sum(data$crisis_aware[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

crisis_aware <- c(crisis_aware_w1y1, crisis_aware_w1y2, crisis_aware_w2y1, crisis_aware_w2y2, crisis_aware_w3y1, crisis_aware_w3y2)

os_learnt_w1y1 <- sum(data$os_learnt[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
os_learnt_w1y2 <- sum(data$os_learnt[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
os_learnt_w2y1 <- sum(data$os_learnt[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
os_learnt_w2y2 <- sum(data$os_learnt[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
os_learnt_w3y1 <- sum(data$os_learnt[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
os_learnt_w3y2 <- sum(data$os_learnt[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

os_learnt <- c(os_learnt_w1y1, os_learnt_w1y2, os_learnt_w2y1, os_learnt_w2y2, os_learnt_w3y1, os_learnt_w3y2)

os_explain_w1y1 <- sum(data$os_explain[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
os_explain_w1y2 <- sum(data$os_explain[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
os_explain_w2y1 <- sum(data$os_explain[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
os_explain_w2y2 <- sum(data$os_explain[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
os_explain_w3y1 <- sum(data$os_explain[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
os_explain_w3y2 <- sum(data$os_explain[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

os_explain <- c(os_explain_w1y1, os_explain_w1y2, os_explain_w2y1, os_explain_w2y2, os_explain_w3y1, os_explain_w3y2)

applicability_w1y1 <- sum(data$applicability[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
applicability_w1y2 <- sum(data$applicability[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
applicability_w2y1 <- sum(data$applicability[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
applicability_w2y2 <- sum(data$applicability[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
applicability_w3y1 <- sum(data$applicability[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
applicability_w3y2 <- sum(data$applicability[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

applicability <- c(applicability_w1y1, applicability_w1y2, applicability_w2y1, applicability_w2y2, applicability_w3y1, applicability_w3y2)

crisis_explain_w1y1 <- sum(data$crisis_explain[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
crisis_explain_w1y2 <- sum(data$crisis_explain[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
crisis_explain_w2y1 <- sum(data$crisis_explain[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
crisis_explain_w2y2 <- sum(data$crisis_explain[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
crisis_explain_w3y1 <- sum(data$crisis_explain[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
crisis_explain_w3y2 <- sum(data$crisis_explain[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

crisis_explain <- c(crisis_explain_w1y1, crisis_explain_w1y2, crisis_explain_w2y1, crisis_explain_w2y2, crisis_explain_w3y1, crisis_explain_w3y2)

crisis_learnt_w1y1 <- sum(data$crisis_learnt[data$Current_Year == "Year 1" & data$timepoint == 1], na.rm = TRUE)
crisis_learnt_w1y2 <- sum(data$crisis_learnt[data$Current_Year == "Year 2" & data$timepoint == 1], na.rm = TRUE)
crisis_learnt_w2y1 <- sum(data$crisis_learnt[data$Current_Year == "Year 1" & data$timepoint == 2], na.rm = TRUE)
crisis_learnt_w2y2 <- sum(data$crisis_learnt[data$Current_Year == "Year 2" & data$timepoint == 2], na.rm = TRUE)
crisis_learnt_w3y1 <- sum(data$crisis_learnt[data$Current_Year == "Year 1" & data$timepoint == 3], na.rm = TRUE)
crisis_learnt_w3y2 <- sum(data$crisis_learnt[data$Current_Year == "Year 2" & data$timepoint == 3], na.rm = TRUE)

crisis_learnt <- c(crisis_learnt_w1y1, crisis_learnt_w1y2, crisis_learnt_w2y1, crisis_learnt_w2y2, crisis_learnt_w3y1, crisis_learnt_w3y2)


data2 <- read.csv(paste(project_path, "/cleaned_data/all_Set2_ConceptualPerception.csv", sep = "")) 
data2$Perception_Score_Mean <- data2$Perception_Score_Total/16
concept_w1y1 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 1" & data2$timepoint == 1], na.rm = TRUE)
concept_w1y2 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 2" & data2$timepoint == 1], na.rm = TRUE)
concept_w2y1 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 1" & data2$timepoint == 2], na.rm = TRUE)
concept_w2y2 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 2" & data2$timepoint == 2], na.rm = TRUE)
concept_w3y1 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 1" & data2$timepoint == 3], na.rm = TRUE)
concept_w3y2 <- mean(data2$Perception_Score_Mean[data2$Current_Year == "Year 2" & data2$timepoint == 3], na.rm = TRUE)

concept <- c(concept_w1y1, concept_w1y2, concept_w2y1, concept_w2y2, concept_w3y1, concept_w3y2)

data3 <- read.csv(paste(project_path, "/cleaned_data/all_Set2_SituationalPerception.csv", sep = "")) 
data3$Knowledge_Score_Mean <- data3$Knowledge_Score_Total/8
situational_w1y1 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 1" & data3$timepoint == 1], na.rm = TRUE)
situational_w1y2 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 2" & data3$timepoint == 1], na.rm = TRUE)
situational_w2y1 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 1" & data3$timepoint == 2], na.rm = TRUE)
situational_w2y2 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 2" & data3$timepoint == 2], na.rm = TRUE)
situational_w3y1 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 1" & data3$timepoint == 3], na.rm = TRUE)
situational_w3y2 <- mean(data3$Knowledge_Score_Mean[data3$Current_Year == "Year 2" & data3$timepoint == 3], na.rm = TRUE)

situational <- c(situational_w1y1, situational_w1y2, situational_w2y1, situational_w2y2, situational_w3y1, situational_w3y2)

data4 <- read.csv(paste(project_path, "/cleaned_data/all_Set2_Awareness.csv", sep = "")) 
awareness_w1y1 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 1" & data4$timepoint == 1], na.rm = TRUE)
awareness_w1y2 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 2" & data4$timepoint == 1], na.rm = TRUE)
awareness_w2y1 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 1" & data4$timepoint == 2], na.rm = TRUE)
awareness_w2y2 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 2" & data4$timepoint == 2], na.rm = TRUE)
awareness_w3y1 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 1" & data4$timepoint == 3], na.rm = TRUE)
awareness_w3y2 <- mean(data4$Awareness_Score_Total[data4$Current_Year == "Year 2" & data4$timepoint == 3], na.rm = TRUE)

awareness <- c(awareness_w1y1, awareness_w1y2, awareness_w2y1, awareness_w2y2, awareness_w3y1, awareness_w3y2)

data5 <- read.csv(paste(project_path, "/cleaned_data/all_Set2_Experience.csv", sep = "")) 
experience_w1y1 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 1" & data5$timepoint == 1], na.rm = TRUE)
experience_w1y2 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 2" & data5$timepoint == 1], na.rm = TRUE) 
experience_w2y1 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 1" & data5$timepoint == 2], na.rm = TRUE)
experience_w2y2 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 2" & data5$timepoint == 2], na.rm = TRUE)
experience_w3y1 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 1" & data5$timepoint == 3], na.rm = TRUE)
experience_w3y2 <- mean(data5$Experience_Score_Total[data5$Current_Year == "Year 2" & data5$timepoint == 3], na.rm = TRUE)

experience <- c(experience_w1y1, experience_w1y2, experience_w2y1, experience_w2y2, experience_w3y1, experience_w3y2)

descriptives <- as.data.frame(rbind(crisis_aware, os_learnt, os_explain, applicability, crisis_explain, crisis_learnt, concept, situational, awareness, experience))

colnames(descriptives) <- c("W1Year1", "W1Year2", "W2Year1", "W2Year2", "W3Year1", "W3Year2")

View(descriptives)
